---
title: "RXX Exercise"
author: "Your Name"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: default
  pdf_document: default
---

# Task 1 

Create a vector called `myVector` and have it store the integers 1, 1 and 1 with `rep()`.

```{r vector, eval=TRUE, echo=TRUE}
myVector <- rep(1,3)
```

# Task 2

Store your answer in `myAnswer`. 

```{r string, eval=T, echo=T}
myAnswer <- "Marco"
```

# Options in Code Chunks (The Racoon)

Explore code chunk options. In order to center the plot, use `fig.align = 'center'` as an option of the code chunk. Usually, people are less interested in R code, and more interested in sweat racoons. Use `echo = FALSE` in order to suppress the code. Same goes for `warning = FALSE` and `message=FALSE`. 

```{r figure-fun, fig.align = 'center', warning=FALSE, message=FALSE, eval=T, echo=F}
# code comes from this post on stackoverflow:
# https://stackoverflow.com/questions/9917049/inserting-an-image-to-ggplot2

library(ggplot2)
library(cowplot)
library(magick)

theme_set(theme_cowplot())

my_plot <-
  ggplot(data    = iris,
         mapping = aes(x    = Sepal.Length,
                       fill = Species)) +
  geom_density(alpha = 0.7)

ggdraw() +
  draw_image("https://i.stack.imgur.com/WDOo4.jpg?s=328&g=1") +
  draw_plot(my_plot)
```

The overall task is to run this code and only show the result. 

# Knitting

When you are done with the tasks, *knit* your document in order to create a HTML file. 

